---
title: "linear model with pred"
author: "Dr. J"
date: "2023-10-17"
output: html_document
---

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE) 
```


## Model1
find an equation that expresses SIMS as a function of ARM

## Results

### Graphical Results

```{r}
plot(SIMS~ARM,data=data)
```

AS arm strength increases, sim score increases.   There is a positive trend between arm strength and sim score. 

### Numerical Results


```{r}
cor(data$SIMS, data$ARM)
```
we have a positive correlation, with noise.


### inference 

```{r}
model1 <- lm(SIMS~ARM,data=data)
summary.lm(model1)
```


```{r}
model1 <- lm(SIMS~ARM,data=data)
plot(data$SIMS~data$ARM)
abline(model1, col='red')
```

for an increase of 1 in arm strength, sim score increases by 0.0545
